### 2020-03-09 figheatmap_R0.tex
new fig

% Created by tikzDevice version 0.12.3 on 2020-03-09 11:51:36
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (110.31, 35.04) {overestimated};
\definecolor{drawColor}{gray}{0.20}

>>>>

% Created by tikzDevice version 0.12.3 on 2020-03-09 12:40:36
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (181.30, 60.59) {$\mathcal{R}_0=2.5$};

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (110.31, 35.04) {overestimated};

\path[draw=drawColor,line width= 1.5pt,line join=round,line cap=round] ( 55.10,177.16) --
	( 64.23,161.35) --
	( 45.97,161.35) --
	( 55.10,177.16);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.71] at ( 55.10,150.58) {$\mathcal{R}_0=2.0$};

\path[draw=drawColor,line width= 1.5pt,line join=round,line cap=round] (315.64,166.62) circle (  6.78);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.71] at (315.64,150.58) {$\mathcal{R}_0=3.1$};
\definecolor{drawColor}{gray}{0.20}
